Supplemental Materials: Bayesian Analysis Overview

### 2020-04-28 paper/manuscript.Rmd
anonymous view-only links for blind peer review

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4995"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
header-includes:
  - \usepackage{float}
documentclass     : "apa6"
csl: apa6.csl
classoption       : "man"
output            : papaja::apa6_pdf
appendix: "appendix.Rmd"
---

@@

Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

@@

## Results and Discussion

@@

[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf)

@@

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot). 
Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.

@@

[^5]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf).

@@

```{r e2token-type, include=F}
# NOT INCLUDED
e2typ <- e2ld %>% group_by(Condition) %>%
  tidyboot_mean(types)

e2types <- ggplot(e2typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=e2ld, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Word Types per Minute") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

#multiplot(e2tokens, e2types, cols=2)
```

@@

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".

@@

e2cja_age = ggplot(e2ja, aes(x = age, y = cja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
  langcog::scale_colour_solarized() + ggthemes::theme_few()

@@

```{r echo = FALSE, results = 'asis'}
render_appendix('appendix.Rmd')
```

```{r echo = FALSE, results = 'asis'}
render_appendix('appendix.Rmd')
```

>>>>

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4995"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
header-includes:
  - \usepackage{float}
documentclass     : "apa6"
csl: apa6.csl
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2020]. 
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment ([see SI](https://osf.io/2bpdf/?view_only=69c0c6ca5d2649438e8642a57671ba79)).

@@

## Results

@@

[^3]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982)

@@

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp1_characteristic_chart.html) for the interactive corpus characteristic plot). 
Words that were strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that were most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.

@@

[^5]: Preregistration: [https://osf.io/6k9m8/](https://osf.io/6k9m8/?view_only=d4b230deba2a4f91bdb2aba29088d982).

@@

@@

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions ([see SI](https://osf.io/2bpdf/files/github/language_analyses/Exp2_characteristic_chart.html)).
The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".

@@

e2cja_age = ggplot(e2ja, aes(x = Age, y = cja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
  langcog::scale_colour_solarized() + ggthemes::theme_few()

@@

### 2020-04-28 paper/manuscript.tex
anonymous view-only links for blind peer review

\abstract{
Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
The rise of phone- and tablet-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions.
We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention.
Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.

@@

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

@@

\hypertarget{results-and-discussion-1}{%
\subsection{Results and Discussion}\label{results-and-discussion-1}}

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf. int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.58{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf. int.: {[}2.83, 3.57{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), 89\% CI = {[}0.18, 0.84{]}, \emph{pd} = 0.99), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf. int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.12, 2.60{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.57\), 89\% CI = {[}-2.42, -0.65{]}, \emph{pd} = 1).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.69\), 89\% CI = {[}0.34, 2.98{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 89\% CI = {[}0.13, 0.77{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
There was an interaction of age and condition (\(\beta=1.59\), 89\% CI = {[}0.35, 2.94{]}, \emph{pd} = 0.98), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.
Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.54, -0.2{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.92\), 89\% CI = {[}-9.85, -1.83{]}, \emph{pd} = 0.99).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

@@

\leavevmode\hypertarget{ref-Baldwin1991}{}%
Baldwin, D. (1991). Infants' contribution to the achievement of joint reference. \emph{Child Development}, \emph{62}, 875--890.

@@

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\hypertarget{experiment-1-activities}{%
\subsection{Experiment 1 Activities}\label{experiment-1-activities}}

\hypertarget{video-a-6-11.9-months-pick-it-up}{%
\subsubsection{Video A (6-11.9 months) ``Pick it
up''}\label{video-a-6-11.9-months-pick-it-up}}

Parents are told to encourage their child to pick up and drop individual
objects. They are also encouraged to place toys on a small cloth and
show the child that they can drag the cloth towards them to reach the
toys.

Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car

\hypertarget{video-b-6-11.9-months-animal-sounds}{%
\subsubsection{Video B (6-11.9 months) ``Animal
sounds''}\label{video-b-6-11.9-months-animal-sounds}}

Parents are told to call different animals and imitate different sounds
the animals make. They are also encouraged to observe which animal the
child prefers.

Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls

\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video C (12-17.9 months) ``Give me the
toy''}\label{video-c-12-17.9-months-give-me-the-toy}}

Parents are told to ask their child to hand over individual toys. They
are also encouraged to praise the child after they give them the toys,
and repeat the process until the child follows the verbal instructions.

Props: toy boat, plastic frog, plastic elephant, toy bus

\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video D (12-17.9 months) ``Classifying my
toys''}\label{video-d-12-17.9-months-classifying-my-toys}}

Parents are told to place toys of different sizes (big or small) in two
hoops. They are also encouraged to ask their child to distinguish
between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small
horse

\hypertarget{video-e-18-23.9-months-my-toys}{%
\subsubsection{Video E (18-23.9 months) ``My
toys''}\label{video-e-18-23.9-months-my-toys}}

Parents are told to show the child toys of the same shape but different
sizes, to place one of the objects in a basket and to ask the child to
take out the object. They are also encouraged to ask their child if the
object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

\hypertarget{video-f-18-23.9-months-the-orchestra}{%
\subsubsection{Video F (18-23.9 months) ``The
orchestra''}\label{video-f-18-23.9-months-the-orchestra}}

Parents are told to give their child a musical instrument to play. They
are also encouraged to play a song and see if the child follows the
rhythm.

Props: maracas, drum, tambourine, clapper

\hypertarget{experiment-2-activities}{%
\subsection{Experiment 2 Activities}\label{experiment-2-activities}}

\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video A (12-17.9 months) ``Give me the
toy''}\label{video-a-12-17.9-months-give-me-the-toy}}

Parents are told to ask their child to hand over individual toys. They
are also encouraged to praise the child after they give them the toys,
and repeat the process until the child follows the verbal instructions.

Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow

\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video B (12-17.9 months) ``Classifying my
toys''}\label{video-b-12-17.9-months-classifying-my-toys}}

Parents are told to place toys of different sizes (big or small) in two
hoops. They are also encouraged to ask their child to distinguish
between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small
horse

\hypertarget{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}{%
\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigsaw
puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}}

Parents are told to encourage their child to name different shapes on a
jigsaw puzzle. Then they are told to undo the puzzle and invite the
child to complete the puzzle.

Props: A jigsaw puzzle of geometric shapes

\hypertarget{video-d-18-23.9-months-my-toys}{%
\subsubsection{Video D (18-23.9 months) ``My
toys''}\label{video-d-18-23.9-months-my-toys}}

Parents are told to show the child toys of the same shape but different
sizes, to place one of the objects in a basket and to ask the child to
take out the object. They are also encouraged to ask their child if the
object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

\hypertarget{video-e-18-23.9-months-the-orchestra}{%
\subsubsection{Video E (18-23.9 months) ``The
orchestra''}\label{video-e-18-23.9-months-the-orchestra}}

Parents are told to give their child a musical instrument to play. They
are also encouraged to play a song and see if the child follows the
rhythm.

Props: maracas, drum, tambourine, clapper

\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
\subsubsection{Video F (18-23.9 months) ``My yellow
toys''}\label{video-f-18-23.9-months-my-yellow-toys}}

Parents are told to show their child yellow toys and to ask, ``What
color are they?'' They are also told to give the child toys of different
colors, to ask them to only play with the yellow ones, and to praise the
child after they do so.

Props: blue car, yellow car, yellow block, red block, blue block, green
block
\end{appendix}

>>>>

\abstract{
Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
The rise of phone-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions.
We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.23, 95\% conf. int.: {[}3.85, 4.65{]}; \(\beta=1.05\), 89\% CI = {[}0.53, 1.56{]}, \emph{pd} = 1) than after the Science Video (mean: 3.19, 95\% conf. int.: {[}2.83, 3.57{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.51\), 89\% CI = {[}0.18, 0.85{]}, \emph{pd} = 0.99), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.88, 95\% conf. int.: {[}2.61, 3.17{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.12, 2.60{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.60\), 89\% CI = {[}-2.46, -0.7{]}, \emph{pd} = 0.99).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.73\), 89\% CI = {[}0.36, 3.06{]}, \emph{pd} = 0.98): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.47\), 89\% CI = {[}0.14, 0.78{]}, \emph{pd} = 0.99), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.19, 95\% CI: {[}1.93, 2.46{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.52, 1.93{]}).
There was an interaction of age and condition (\(\beta=1.64\), 89\% CI = {[}0.42, 2.95{]}, \emph{pd} = 0.99), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.
Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.89\), 89\% CI = {[}-1.52, -0.19{]}, \emph{pd} = 0.98), and spent more time in passive JA with their caregiver (\(\beta=-5.96\), 89\% CI = {[}-9.82, -1.98{]}, \emph{pd} = 0.99).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

@@

@@

### 2020-04-28 paper/supp-Bayesian-analyses.Rmd
anonymous view-only links for blind peer review

---
title: 'Appendix: Bayesian Analysis Overview'
output: pdf_document
---

@@

```{r, parent-ed-effect, echo=F, fig.cap="Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
dat = types_modE %>% posterior_samples("parent_ed") %>%
  estimate_density(extend=TRUE)

@@

```{r, plot-posteriors, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}
plot_posterior(types_modE, title="Exp. 1: Word Types")
```

```{r, plot-token-posterior, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}

@@

```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting TTR, with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown.", warning=F}
plot_posterior(ttr_modE1, "Exp. 1: TTR")
```

```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting MTLD, with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}
plot_posterior(mtld_modE1, "Exp. 1: MTLD")
```

>>>>

---
title: 'Supplemental Materials: Bayesian Analysis Overview'
output: pdf_document
---
<!-- 424 words -->

@@

```{r, parent-ed-effect, echo=F, fig.cap="Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0, warning=F}
dat = types_modE %>% posterior_samples("parent_ed") %>%
  estimate_density(extend=TRUE)

@@

```{r, plot-posteriors, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown.", warning=F}
plot_posterior(types_modE, title="Exp. 1: Word Types")
```

```{r, plot-token-posterior, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown.", include=F}

@@

```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting TTR, with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown.", warning=F, include=F}
plot_posterior(ttr_modE1, "Exp. 1: TTR")
```

```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting MTLD, with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown.", include=F}
plot_posterior(mtld_modE1, "Exp. 1: MTLD")
```
